---
title: "getting environmental data"
author: "Andrew Nguyen"
date: "2015-July-08"
output: pdf_document
---
libraries
```{r load libraries,echo=FALSE,include=FALSE}
library(lattice)
library(permute)
library(vegan)
library(MASS)
library(sp)
library(raster)
library(rgdal) 
library(dismo)
library(maptools)
library(foreign)
library(grid)
library(lattice)
library(maps)
library(ape)
#library(leaps)
library(QuantPsyc)
library(ggplot2)
library(MuMIn)
library(plyr)
library(dplyr)
options(na.action = "na.fail")
```

BIO1 = Annual Mean Temperature
BIO2 = Mean Diurnal Range (Mean of monthly (max temp - min temp))
BIO3 = Isothermality (BIO2/BIO7) (* 100)
BIO4 = Temperature Seasonality (standard deviation *100)
BIO5 = Max Temperature of Warmest Month
BIO6 = Min Temperature of Coldest Month
BIO7 = Temperature Annual Range (BIO5-BIO6)
BIO8 = Mean Temperature of Wettest Quarter
BIO9 = Mean Temperature of Driest Quarter
BIO10 = Mean Temperature of Warmest Quarter
BIO11 = Mean Temperature of Coldest Quarter
BIO12 = Annual Precipitation
BIO13 = Precipitation of Wettest Month
BIO14 = Precipitation of Driest Month
BIO15 = Precipitation Seasonality (Coefficient of Variation)
BIO16 = Precipitation of Wettest Quarter
BIO17 = Precipitation of Driest Quarter
BIO18 = Precipitation of Warmest Quarter
BIO19 = Precipitation of Coldest Quarter
```{r}
merg<-read.csv("../Data/2015_id_colony_species_rearingtemp.csv")
w <- getData('worldclim', var='bio', res=2.5)
dbio1 <- extract(w, merg[,c("lon.2","lat")])

env<-princomp(dbio1[,1:6])
summary(env)
loadings(env)

R<-as.data.frame(cbind(merg,dbio1))
write.csv(R,"2015_JSG_phytotron_bioclim.csv")
```


### Gettign elevational data
```{r}
ss<-read.csv("Sampling_sites_table.csv")


#http://stackoverflow.com/questions/21593868/extracting-elevation-from-website-for-lat-lon-points-in-australia-using-r

googEl <- function(locs)  {
  require(RJSONIO)
  locstring <- paste(do.call(paste, list(locs[, 2], locs[, 1], sep=',')),
                     collapse='|')
  u <- sprintf('http://maps.googleapis.com/maps/api/elevation/json?locations=%s&sensor=false',
               locstring)
  res <- fromJSON(u)
  out <- t(sapply(res[[1]], function(x) {
    c(x[['location']]['lat'], x[['location']]['lng'], 
      x['elevation'], x['resolution']) 
  }))    
  rownames(out) <- rownames(locs)
  return(out)
}

a<-t(as.data.frame(googEl(ss[,c("Longitude","Latitude")])[,3]))
ng<-data.frame(cbind(ss,a))
write.csv(ng,"20161026_samplingdata_with_elevation.csv")
```