---
title: "Evolution of Stress response in Aphaenogaster"
author: "Andrew Nguyen"
date: "2015-August-25"
output: pdf_document
---

#How does the stress response evolve in organisms(ants) that experience varying thermal environments?

Hypothesis: Ants elicit the stress response that match their local thermal environments, indicative of local adaptation.

Prediction: There should be clinal variation in the stress response across A. picea/rudis'.

Methods: We collected along a N-S transect from Florida to Maine and measured their stress response under a common garden experiment. In total, we sampled 27 unique sites and collected 74 colonies. To determine whetherWe measured the stress response quantifying the basal and induction gene expression patterns of three heat shock proteins (hsc70, hsp83, hsp40) for each colony. The degree of induction was measured as the relative fold increase of mildly heat treated (37C) compared to control treated(25C) ants. 

In total, there were 64 colonies, 37 of which reared at 20C and 27 reared at 26C.

###20150824 update: Including phylogenetic relationships into regressions

###20150825 meeting: use forward selection with AIC instead of model averaging; Bible(primer of ecological statistics) pg 346

###20150826 update: identified error(wrong CT value) for hsp70 basal xp in sample 5-B.

```{r load libraries, echo=FALSE,include=FALSE}
library(plyr)
library(dplyr)
library(MuMIn)
options(na.action = "na.fail")
library(ape)
library(MASS)
library(ggplot2)
library(gridExtra)
library(raster)
library(rgdal) 
library(dismo)
library(maptools)
library(mapdata)
```
#Data parsing
```{r data parsing}
dat<-read.csv("../Data/20150810_anbe_curated_dat_v3.csv",skip=6) #xp data
dat2<-read.csv("../Data/2015_JSG_phytotron_bioclim.csv") # full data set with climate factors
#changing factors into characters for Colony so I can merg em!
dat$Colony<-as.factor(as.character(dat$Colony))
dat2$Colony<-as.factor(as.character(dat2$Colony))

#merging dat and dat2 so I can link up xp data with climate factors!
merg<-inner_join(dat2,dat,by="Colony")
#summary of data
dim(merg) # dimensions of dataset
summary(merg$Species_2)# number of species

summary(as.factor(as.character(merg$Rearing_Temp)))#the number of colonies reared at 20 and 26
knitr::kable(subset(merg,merg$Species_2=="fulva")[,1:14] )# just seeing what fulva looks like

#reading in phylogenetic tree 
#jsg.tree<-read.tree("../Phylogenetics/20150824_JSG_phytotron_tree_BL_only_v2")
jsg.tree<-read.tree("../Data/Phylogenetics/20150824_JSG_phytotron_tree_BL_only_v2")
#"28-A"
jsg.tree<-drop.tip(jsg.tree,tip=c("28-A","11-C","25-C","07-B","10-F"))
plot(jsg.tree)
write.tree(jsg.tree,"20161012_Hsp_modulation_phylogeny.newick")
#newblife<-read.tree("Phylogenetics/20150824_JSG_phytotron_tree_BL_only_v3_20150219_renamed_pub_fig_noBR1_v2")
#newblife2<-drop.tip(newblife,tip=c("BR1"))
#plot(newblife2)
#write.tree(newblife2,"20150824_JSG_phytotron_tree_BL_only_v3_20150219_renamed_pub_fig_noBR1_v3")
#length(newblife2$tip.label);length(newblife2$tip.label)
pcoa.jsg<-pcoa(cophenetic.phylo(jsg.tree))
biplot(pcoa.jsg) #viewing separation 

#setting as dataframe
n.pcoa.jsg<-as.data.frame(pcoa.jsg$vectors[,1:4])
n.pcoa.jsg$Colony<-jsg.tree$tip.label
dim(n.pcoa.jsg)
##making full dataset
merg<-inner_join(merg,n.pcoa.jsg,by="Colony")
names(merg)
names(merg)[44:46]<-c("Axis.1","Axis.2","Axis.3")
dim(merg)# nice!!
summary(as.factor(as.character(merg$Rearing_Temp)))
ful<-subset(merg,merg$Species_2=="fulva")

ddply(merg,.(Site),summarize,count=length(Colony))#counts of colonies at each site
plot(merg$Axis.1,merg$Axis.2,xlim=c(-.15,.25),ylim=c(-.25,.1),type="n",xlab="Axis 1",ylab="Axis 2")
text(merg$Axis.1,merg$Axis.2,labels=merg$Tree_site)

plot(merg$Axis.2,merg$Axis.3,type="n",xlab="Axis 2",ylab="Axis 3",xlim=c(-.05,.1))
text(merg$Axis.2,merg$Axis.3,labels=merg$Tree_site)

```

#checking axes
```{r checking axes}
#phylo.70.1<-lm(log10(merg$FC_70)~merg$Axis.1)
#hist(resid(phylo.70.1),xlim=c(-.8,.8))


phylo.70.2<-lm(log10(merg$FC_70)~merg$Axis.1+merg$Axis.2)
hist(resid(phylo.70.2),xlim=c(-.8,.8))

phylo.70.3<-lm(log10(merg$FC_70)~merg$Axis.1+merg$Axis.2+merg$Axis.3)
hist(resid(phylo.70.3))

```

#Stats: Using forward selection
response: basal or induction gene xp--log10 transformed to meet the assumptions of normality
predictors: rearing temp, Tmax(bio5)
```{r forward model selection}
#applying a regression model across columns
#response: basal or induction gene xp
#predictors: rearing temp, bio1(MAT)
mergy<-merg[-57,]

##induction
#hsp70 induction
full.70<-lm(log10(merg$FC_70)~merg$bio5+merg$Rearing_Temp+merg$Axis.1+merg$Axis.2+merg$Axis.3)
summary(stepAIC(full.70,direction="forward"))
boxplot(log10(FC_70)~Rearing_Temp,data=merg)
#hsp83 induction
full.83<-lm(log10(merg$FC_83)~merg$bio5+merg$Rearing_Temp+merg$Axis.1+merg$Axis.2+merg$Axis.3)
summary(stepAIC(full.83,direction="forward"))
gg<-dredge(full.83)
boxplot(FC_83~Rearing_Temp,data=merg)
#write.csv(subset(merg,merg$FC_83>10),"test.csv")
#hsp40 induction
full.40<-lm(log10(mergy$FC_40)~mergy$bio5+mergy$Rearing_Temp+mergy$Axis.1+mergy$Axis.2+mergy$Axis.3)
summary(stepAIC(full.40,direction="forward"))
#aov_40_induction<-aov(log10(mergy$FC_40)~mergy$Rearing_Temp)
#summary(aov_40_induction)
#plot(aov_40_induction)

#looks good

#removing influental sample # 48
#out_48_for_hsp40<-mergy[-48,]
#sub_40<-lm(log10(out_48_for_hsp40$FC_40)~out_48_for_hsp40$bio5+out_48_for_hsp40$Rearing_Temp+out_48_for_hsp40$Axis.1+out_48_for_hsp40$Axis.2+out_48_for_hsp40$Axis.3)
#summary(stepAIC(sub_40,direction="forward"))

########################

#basal
#hsp70
B.70<-lm(log10(merg$B_70)~merg$bio5+merg$Rearing_Temp+merg$Axis.1+merg$Axis.2+merg$Axis.3)
summary(stepAIC(B.70,direction="forward"))
boxplot(log10(merg$B_70)~merg$Rearing_Temp,ylab="log10 transformed fold change",las=1,xlab="rearing temp")

########################
par(mfrow=c(2,2))
plot(B.70)
par(mfrow=c(1,1))
#hsp83
B.83<-lm(log10(merg$B_83)~merg$bio5+merg$Rearing_Temp+merg$Axis.1+merg$Axis.2+merg$Axis.3)
summary(stepAIC(B.83,direction="forward"))
#boxplot(log10(merg$B_83)~merg$Rearing_Temp) #doesn't look real
#hsp40

B.40<-lm(log10(B_40)~bio5+Rearing_Temp+Axis.1+Axis.2+Axis.3,data=merg)
summary(stepAIC(B.40,direction="forward"))

####two panel figurse for hsp70 basal and hsp40 induction!
#side by side plot
#grid.arrange(basal_70,induc_hsp40,ncol=2)
#stacked plot
#new_hsp70<-basal_70+xlab("")
#grid.arrange(new_hsp70,induc_hsp40,nrow=2)
# effect of MAT on hsp gxp
apply(merg[,38:43],2,function(x){summary(stepAIC(lm(log10(x)~merg$bio5+merg$Rearing_Temp+merg$Axis.1+merg$Axis.2+merg$Axis.3)),direction="forward")})


apply(mergy[,38:43],2,function(x){summary(stepAIC(lm(log10(x)~mergy$bio1+mergy$Rearing_Temp+mergy$Axis.1+mergy$Axis.2+mergy$Axis.3)),direction="forward")})

apply(mergy[,38:43],2,function(x){summary(stepAIC(lm(log10(x)~mergy$bio5+mergy$Rearing_Temp+mergy$Axis.2+mergy$Axis.3)),direction="forward")})
```

#Mean expression values
```{r mean expression values}
## overall mean
knitr::kable(as.data.frame(apply(mergy[,38:43],2,mean)))


dim(mergy)
F<-c(rep("FC_83",56),rep("FC_70",56),rep("FC_40",56))
nn<-data.frame(cbind(F,c(mergy[,38],mergy[,39],mergy[,40])))
nn$V2<-as.numeric(as.character(nn$V2))
summary(aov(V2~F,data=nn))
##by rearing temp
c<-ddply(merg,.(Rearing_Temp),summarize, Induction83=mean(FC_83),Basal83=mean(B_83),Induction70=mean(FC_70),Basal70=mean(B_70))

i<-ddply(mergy,.(Rearing_Temp),summarize,Induction40=mean(FC_40),Basal40=mean(B_40))

da<-cbind(c,i[,2:3])

#table of means
knitr::kable(da)


#median expression
cc<-ddply(merg,.(Rearing_Temp),summarize, Induction83=median(FC_83),Basal83=median(B_83),Induction70=median(FC_70),Basal70=median(B_70))

ii<-ddply(mergy,.(Rearing_Temp),summarize,Induction40=median(FC_40),Basal40=median(B_40))
#medians
medians<-cbind(cc,ii[,2:3])
```

#Expression Figures for rearing temp
```{r rearing temp figures}
#theme########################################
T<-theme_bw()+theme(text=element_text(size=30),axis.text=element_text(size=30),legend.text=element_text(size=28),panel.grid.major=element_blank(),panel.grid.minor.x = element_blank(),panel.grid = element_blank(),legend.key = element_blank())

dude<-scale_fill_manual(name = "", values = c("gray", "goldenrod"))
#color
##################################################
#####ggplot of hsp83 basal
#add notches: geom_boxplot(notch=TRUE)
basal_83<-ggplot(data=merg,aes(x=factor(Rearing_Temp),y=B_83,fill=factor(Rearing_Temp)))+geom_boxplot()+T+ylab(expression(paste("Hsp83 basal expression (",2^paste(Delta,Delta,"CT"),")")))+scale_y_continuous(limits=c(0,7),breaks=seq(0,7,1))+xlab("")+dude+guides(fill=FALSE)

#+xlab("Maintenance Temperature (°C)")
basal_83

#####ggplot of hsp70 basal
basal_70<-ggplot(data=merg,aes(x=factor(Rearing_Temp),y=B_70,fill=factor(Rearing_Temp)))+geom_boxplot()+T+ylab(expression(paste("Hsp70 basal expression (",2^paste(Delta,Delta,"CT"),")")))+scale_y_continuous(limits=c(0,8),breaks=seq(0,8,2))+xlab("")+dude+guides(fill=FALSE)
#+xlab("Maintenance Temperature (°C)")
basal_70
#####ggplot of hsp40 basal
basal_40<-ggplot(data=mergy,aes(x=factor(Rearing_Temp),y=B_40,fill=factor(Rearing_Temp)))+geom_boxplot()+ylab(expression(paste("Hsp40 basal expression (",2^paste(Delta,Delta,"CT"),")")))+scale_y_continuous(limits=c(0,11),breaks=seq(0,11,1))+T+xlab("")+dude+guides(fill=FALSE)+xlab("Acclimation Temperature (°C)")
#+xlab("Maintenance Temperature (°C)")+
basal_40

#####ggplot of hsp83 induction
induc_hsp83<-ggplot(data=merg,aes(x=factor(Rearing_Temp),y=FC_83,fill=factor(Rearing_Temp)))+geom_boxplot()+T+xlab("")+ylab(expression(paste("Hsp83 induction (",2^paste(Delta,Delta,"CT"),")")))+dude+guides(fill=FALSE)
induc_hsp83

#####ggplot of hsp70 induction
induc_hsp70<-ggplot(data=merg,aes(x=factor(Rearing_Temp),y=FC_70,fill=factor(Rearing_Temp)))+geom_boxplot()+T+xlab("")+ylab(expression(paste("Hsp70 induction (",2^paste(Delta,Delta,"CT"),")")))+dude+guides(fill=FALSE)
induc_hsp70
#####ggplot of hsp70 induction
#####ggplot of hsp40 induction
induc_hsp40<-ggplot(data=mergy,aes(x=factor(Rearing_Temp),y=FC_40,fill=factor(Rearing_Temp)))+geom_boxplot()+T+xlab("Acclimation Temperature (°C)")+ylab(expression(paste("Hsp40 induction (",2^paste(Delta,Delta,"CT"),")")))+T+dude+guides(fill=FALSE)
induc_hsp40
#+scale_y_continuous(limits=c(0,8),breaks=seq(0,8,2))


#grid.arrange(basal_83,basal_70,basal_40,induc_hsp83,induc_hsp70,induc_hsp40,nrow=2,ncol=3)

grid.arrange(basal_83,induc_hsp83,basal_70,induc_hsp70,basal_40,induc_hsp40,nrow=3,ncol=2)

```
#Expression figures against Tmax
```{r expression figs against Tmax}
T<-theme_bw()+theme(text=element_text(size=30),axis.text=element_text(size=30),legend.text=element_text(size=28),panel.grid.major=element_blank(),legend.position="none",panel.grid.minor.x = element_blank(),panel.grid = element_blank(),legend.key = element_blank())
#loess fit
#loess<-stat_smooth(colour="red",geom="smooth",method="auto",se=FALSE,size=3)
loess<-stat_smooth(colour="red",method="loess",span=1)
#merg$bio5<-merg$bio5/10

######hsp83 basal###############
T83<-ggplot(data=merg,aes(x=bio5/10,y=B_83))+geom_point(size=5)+T+ylab(expression(paste("Hsp83 basal expression (",2^paste("-",Delta,Delta,"CT"),")")))+scale_y_continuous(limits=c(0,7),breaks=seq(0,7,1))+xlab("")
#+loess
T83

######hsp70 basal###############
T70<-ggplot(data=merg,aes(x=bio5/10,y=B_70))+geom_point(size=5)+T+ylab(expression(paste("Hsp70 basal expression (",2^paste("-",Delta,Delta,"CT"),")")))+scale_y_continuous(limits=c(0,7),breaks=seq(0,7,1))+xlab("")
#+loess
T70

######hsp40 basal###############
#mergy$bio5<-mergy$bio5/10
T40<-ggplot(data=mergy,aes(x=bio5/10,y=B_40))+geom_point(size=5)+T+ylab(expression(paste("Hsp40 basal expression (",2^paste("-",Delta,Delta,"CT"),")")))+scale_y_continuous(limits=c(0,11),breaks=seq(0,11,1))+xlab("Tmax (°C)")
#+loess
T40

#####################
######hsp83 induction###############
T83ind<-ggplot(data=merg,aes(x=bio5/10,y=FC_83))+geom_point(size=5)+T+ylab(expression(paste("Hsp83 induction (",2^paste("-",Delta,Delta,"CT"),")")))+scale_y_continuous(limits=c(0,44),breaks=seq(0,44,4))+xlab("")
#+loess
T83ind

######hsp70 induction###############
T70ind<-ggplot(data=merg,aes(x=bio5/10,y=FC_70,))+geom_point(size=5)+T+ylab(expression(paste("Hsp70 induction (",2^paste("-",Delta,Delta,"CT"),")")))+scale_y_continuous(limits=c(10,120),breaks=seq(10,120,10))+xlab("")
#+loess
T70ind

######hsp40 induction###############
T40ind<-ggplot(data=mergy,aes(x=bio5/10,y=FC_40))+geom_point(size=5)+T+ylab(expression(paste("Hsp40 induction (",2^paste("-",Delta,Delta,"CT"),")")))+scale_y_continuous(limits=c(0,44),breaks=seq(0,44,4))+xlab("Tmax (°C)")
#+loess
T40ind

#grid.arrange(T83,T70,T40,T83ind,T70ind,T40ind,nrow=2,ncol=3)
grid.arrange(T83,T70,T40,nrow=3)
grid.arrange(T83ind,T70ind,T40ind,nrow=3)
```
#Hsp40 vs Axis 3
```{r hsp40 v axis3,eval=FALSE}
plot(B_40~Axis.3,data=mergy)
text(mergy$Axis.3,mergy$B_40,labels=mergy$Colony)
#t<-mergy
#hist(mergy$Axis.3)
#regular zoom
plot(mergy$Axis.3,mergy$Axis.2,type="n")
text(mergy$Axis.3,mergy$Axis.2,labels=mergy$Colony)

#zoomed in
plot(mergy$Axis.3,mergy$Axis.2,ylim=c(0.02,0.05))
text(mergy$Axis.3,mergy$Axis.2,labels=mergy$Colony)
#data parsing
mergy<-subset(merg,merg$Axis.2> -0.1)
sub<-subset(merg,merg$Axis.2< -0.1)
sub$axis3_desig<-as.factor(rep("zAxis 2 A. picea",3))
mergy$axis3_desig<-ifelse(mergy$Axis.3<= -0.044,"North",ifelse(mergy$Axis.3>0.05,"South","A. picea"))
mergy<-rbind(mergy,sub)
mergy<-mergy[-54,]
boxplot(log10(B_40)~axis3_desig,data=mergy)
summary(aov(log10(B_40)~axis3_desig,data=mergy))

newb<-subset(mergy,mergy$axis3_desig=="South")
newb2<-subset(mergy,mergy$axis3_desig=="North")
newb3<-as.data.frame(rbind(newb,newb2))
summary(aov(log10(B_40)~axis3_desig,data=mergy))
boxplot(B_40~axis3_desig,data=newb3,las=1,xlab="A. rudis clade (Axis 3)",ylab="log10 Hsp40 Basal expression")

###ggplot fig
Axis3_b40<-ggplot(data=newb3,aes(x=factor(axis3_desig),y=B_40,fill=factor(axis3_desig)))+geom_boxplot()+T+ylab(expression(paste("Hsp40 basal expression (",2^paste(Delta,Delta,"CT"),")")))+scale_y_continuous(limits=c(0,7),breaks=seq(0,7,1))+scale_fill_manual(name = "", values = c("deepskyblue4", "firebrick"))+guides(fill=FALSE)+xlab(expression(paste(italic("A. rudis")," clade (Axis 3)")))
#+xlab("A. rudis clade (Axis 3)")
Axis3_b40

mergy$axis3_desig<-as.factor(mergy$axis3_desig)
###with all 3
Axis3_b40_v2<-ggplot(data=mergy,aes(x=factor(axis3_desig),y=B_40,color=factor(axis3_desig)))+geom_jitter(position=position_jitter(0.1),cex=6)+T+
  ylab(expression(paste("Hsp40 basal expression (",2^paste(Delta,Delta,"CT"),")")))+
  scale_y_continuous(limits=c(0,7),breaks=seq(0,7,1))+
  scale_colour_manual(name = "", values = c("black","deepskyblue4", "firebrick","purple"))+guides(fill=FALSE)+xlab(expression(paste(italic("                     A. rudis")," clade (Axis 3)")))
#+xlab("A. rudis clade (Axis 3)")
Axis3_b40_v2

###v3

#grab medians
meds <- c(by(mergy$B_40, mergy$axis3_desig, median))
means <- c(by(mergy$B_40, mergy$axis3_desig, mean))

Axis3_b40_v3<-ggplot(data=mergy,aes(x=factor(axis3_desig),y=B_40,fill=factor(axis3_desig)))+geom_boxplot()+T+
  ylab(expression(paste("Hsp40 basal expression (",2^paste(Delta,Delta,"CT"),")")))+scale_x_discrete(expression(paste(italic("                     A. rudis")," clade")),labels=expression(paste(italic("                                                    A. picea "),"            North   ","       South ","    Axis 2")))+
  scale_y_continuous(limits=c(-1,11),breaks=seq(0,11,1))+
  scale_fill_manual(name = "", values = c("gray","deepskyblue4", "firebrick","purple"))+guides(fill=FALSE)
Axis3_b40_v3

boxplot(B_40~axis3_desig,data=mergy)
```
#hsp40 vs axis2

```{r hsp40 vs axis2,eval=FALSE}
#regular zoom
plot(mergy$Axis.3,mergy$Axis.2,type="n")
text(mergy$Axis.3,mergy$Axis.2,labels=mergy$Colony)

mergy$desig_axis2<-ifelse(mergy$Axis.2<= -.1,"hybrids","picea/rudis")

par(mar=c(5,5,5,5))
boxplot(B_40~desig_axis2,data=mergy,ylab="hsp40 basal expression",xlab="Axis 2 designations")#looking
boxplot(log10(B_40)~desig_axis2,data=mergy,ylab="Log10 hsp40 basal expression",xlab="Axis 2 designations")#looking


```


#making maps for a talk
##field collections site map
```{r,eval=FALSE}
w <- getData('worldclim', var='bio', res=2.5)

plot(w, 5, xlim=c(-87,-65), ylim=c(30,48), axes=F, legend=T, col=colorRampPalette(c("skyblue","white"))(255),main="",box=FALSE)
#map("world",c("USA","Canada"),add=TRUE)
map("state", c('florida', 'south carolina', 'north carolina', 'georgia', 'virginia', 'west virginia', 'maryland', 'delaware', 'new jersey', 'rhode island', 'new york', 'connecticut', 'massachusetts', 'pennyslvania', 'vermont', 'new hampshire', 'maine', 'alabama', 'tennessee', 'kentucky', 'ohio','iowa','illinois','arkansas','missouri','minnesota','wisconsin','michigan','louisiana','mississippi',"texas","arizona","illinois","california","oregon","utah","washington","kansas","new mexico","montana","idaho","wyoming","north dakota","south dakota","nebraska","oklahoma"), add = TRUE)
rect(-150,25,-55,5,col="white",border="white")
rect(-65,50,-50,25,col="white",border="white")
rect(-87,50,-100,25,col="white",border="white")
bb8<-read.csv("../Data/20160219_site_for_map_excludingsome_v2.csv")
colm<-ifelse(merg$Axis.1>.17,"#D55E00","#0072B2")
points(merg$lon.2,merg$lat,pch=20,col=colm,cex=1.75)
#points(bb8$lon.2,bb8$lat,pch=20,cex=1.5)
text(bb8$lon.3,bb8$lat+.4,labels=bb8$Site_2,cex=.75,font=2)
#plotting points with the size related to thermal niche breadth
#add color by species
#http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/#a-colorblind-friendly-palette



#text(merg$lon.2,merg$lat+.5,labels=merg$Site_2,cex=.75)




```


```{r}
cpsit<-ddply(merg,.(Site_2),summarize,Longitude=mean(lon.2),Latitude=mean(lat),Tmax=mean(bio5))
head(cpsit)
dim(cpsit)

cpsit
new<-cpsit[order(cpsit$Tmax),]
new

#write.csv(new,"Sampling_sites_table.csv")

```

#20160825_sampling map
```{r,eval=FALSE}
fgl<-read.csv("20160825_final_dataset_HSP_modulation.csv")
fgl$tree_color<-as.character(fgl$tree_color)


plot(w, 5, xlim=c(-87,-65), ylim=c(30,48), axes=FALSE, legend=FALSE, col=colorRampPalette(c("skyblue","white"))(255),main="",box=FALSE)
#map("world",c("USA","Canada"),add=TRUE)
map("state", c('florida', 'south carolina', 'north carolina', 'georgia', 'virginia', 'west virginia', 'maryland', 'delaware', 'new jersey', 'rhode island', 'new york', 'connecticut', 'massachusetts', 'pennyslvania', 'vermont', 'new hampshire', 'maine', 'alabama', 'tennessee', 'kentucky', 'ohio','iowa','illinois','arkansas','missouri','minnesota','wisconsin','michigan','louisiana','mississippi',"texas","arizona","illinois","california","oregon","utah","washington","kansas","new mexico","montana","idaho","wyoming","north dakota","south dakota","nebraska","oklahoma"), add = TRUE)
map('lakes', add=TRUE, fill=TRUE, col='white', boundary='black')
rect(-150,25,-55,5,col="white",border="white")
rect(-65,50,-50,25,col="white",border="white")
rect(-87,50,-100,25,col="white",border="white")

points(fgl$lon.2,fgl$lat,col=fgl$tree_color,pch=fgl$pch)
#la<-subset(bb8,bb8$Site=="LA")
points(-79.181,37.4211,pch=19,col="blue")
#text(fgl$lon.3,fgl$lat+.4,labels=fgl$Site_2,cex=.75,font=2)
text(bb8$lon.3,bb8$lat+.4,labels=bb8$Site_2,cex=.75,font=2)

```

#checking correlation between Tmax, MAT, and Phylogenetic Axes
```{r}
names(mergy)
knitr::kable(round(cor(cbind(mergy$bio1,mergy$bio5,mergy[,44:47])),3)) 
```


#Checking basal ct values
```{r}
ct<-read.csv("../Data/20150810_raw_CT_values.csv")

z<-inner_join(ct,mergy,by="Colony")
z$qpcr_block<-as.factor(z$qpcr_block)
#different 18s ct among treatments?
#different 18s ct
summary(stepAIC(lm(log2(X18)~bio5*treatment+qpcr_block+Axis.1+Axis.2+Axis.3+Rearing_Temp,data=z2)),direction="forward")


```

```{r Sessioninfo}
sessionInfo()
```

